Exploring the tree of numerical semigroups

### 2014-09-16 Papier/article.tex
Intro + abstract.

\begin{abstract}
In this paper we describe an algorithm visiting all the numerical semigroups up to a given genus using a new representation of numerical semigroups. 
\end{abstract}

@@

\Jean{Here we describe a new algorithm for the exploration of the tree of numerical semigroup $\mathcal{T}$ and achieve the computation of $n_g$ for $g\leq 67$. 
The cornerstone of our method is a new combinatorial representation of numerical semigroup that is well suited for exploration of the tree~$\mathcal{T}$ and allow code optimization essentially based on use of vectorial instructions and parallelization.}

@@

>>>>

\begin{abstract}
  In this paper we describe an algorithm visiting all the numerical semigroups
  up to a given genus using a new representation of numerical semigroups. The
  interest of this algorithm is that it fits particularly well the
  architecture of modern computer allowing very large optimizations.
\end{abstract}

@@

Here we describe a new algorithm for the exploration of the tree of numerical
semigroup $\mathcal{T}$ and achieve the computation of $n_g$ for $g\leq 67$.
The cornerstone of our method is a new combinatorial representation of
numerical semigroup that is well suited for exploration of the
tree~$\mathcal{T}$ and allow \Florent{large} code optimization essentially based on use of
vectorial instructions and parallelization. \Florent{The goal of the paper is twofold:
first to present our new encoding of the semigroup and the associated
algorithms, and second to present the optimization technique which allows for
those kinds of algorithms to get speedups by factors of hundreds and even
thousand. We claim that these technique are fairly general for those kinds of
algorithms. As a support for the claim, we applied it to an algorithm of
N.~Borie enumerating integer vector modulo permutation groups~\cite{Borie} and
got a speedup by a factor larger than 2000 using 8 cores !}

@@

\bibitem{Borie}{N.~Borie, \emph{Generation modulo the action of a permutation
      group}, Proceeding of The 25th International Conference on Formal Power
    Series and Algebraic Combinatorics (FPSAC '13), DMTCS Proceedings \textbf{0}(01) (2013),
    767--778}
